A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2015-01-08 ms.tex
Added a discussion on possible pitchfork effect found in Pober et al 2013 and Thyagarajan et al 2013.

>>>>

{\bf Interestingly, \citet{thy13} and \citet{pob13} have found a similar feature in their simulations and data respectively. In the latter, this feature is described as ``edge brightening'' and attributed to the Galactic plane near the horizon. From their discussion, it is unclear what fraction of power in that feature arises from ubiquitous diffuse emission unlike in our {\it zenith} pointing where the Galactic plane is not expected to play a significant role. On the other hand, \citet{thy13} statistically modeled point sources below the confusion limit and attributed the feature to an increase in solid angles subtended by delay bins closer to the horizon limits thereby, enhancing the resulting integrated emission. This must be true for diffuse emission as well. Thus we argue the feature arises primarily due to an increase in sensitivity of long baselines to diffuse emission from far off--axis angles caused by foreshortening, and partly due to a higher integrated emission in delay bins close to the horizon limits which map larger solid angles in these directions}.
